\documentclass[11pt]{article}

\title{First Client Meeting}
\author{Alpha Curr}
\date{06 August 2018}

\begin{document}
\maketitle

\section{Present Participants}
Dr. Woolway \\
Lehlohonolo Motsi (1312548)\\
Tlotlang Sekgetho (1432706)\\
Masingita Rikhotso (1272188)\\
Thandi Tshabalala (1472222)

\section{Agenda}
\begin{enumerate}
\item Project description
\item Data collection information
\end{enumerate}

\subsection{Project description}
The project choose by the group is \textbf{Test Date and Class Venue Allocation}.\\
The project involves the creation of a replicate system that is used by PIMD for venue allocations. While PIMD uses does this operation manually we aim to integrate the system and make it electronically.\\
\newline
PIMD deal with venue allocation, they collect information from lectures/administrators regarding what venue they will need for what. The information collected is Course code, days, class size, equipment required, lecture/tutorial. Then from all the information collected a venue is allocated to meet most of the requirements. The system has a list of venues that are available and on proper working condition that can be used. The system the allocate available venues to each course and try to give the best possible optimisation.\\
The system is web-based and for the login process we will be integrating with LDAP, a system used by CNS at Wits to identify students and staff memebers from database entry.

\subsection{Data collection information}
All the data information will be given by PIMD Wits so we do not have to collect it manually.

\section{Next Meeting}
Next meeting scheduled for 13 August 2018.


\end{document}